\begin{thebibliography}{AH89}

\bibitem[LLR05]{Lahl05}
S.~Lahlou, M.~Langheinrich, and C.~R\"{u}cker.
\newblock Privacy and Trust Issues with Invisible Computers.
\newblock {\em Communications of the ACM}, 48(3), 2005.

\bibitem[WL05]{Wang05}
F.~Wang and P.~Liu.
\newblock Temporal Management of RFID Data.
\newblock In {\em Proc. of VLDB}, 2005.

\bibitem[CKRS04]{Chaw04}
S.~Chawathe, V.~Krishnamurthyy, S.~Ramachandrany, and S.~Sarma.
\newblock Managing RFID data.
\newblock In {\em Proc, of VLDB}, 2004.

\bibitem[OA00]{Orr00}
R.J.~Orr and G.D.~Abowd.
\newblock The Smart Floor: A Mechanism for Natural User Identification and Tracking.
\newblock In {\em Proc. of CHI}, 2000.

\bibitem[PORE00]{Post00}
E.R.~Post, M.~Orth, P.R.~Russo, and G.N.~Ebroidery.
\newblock Design and fabrication of textile-based computing.
\newblock {\em IBM Systems Journal}, 39(3\&4), 2000.

\bibitem[POTO04]{Potonni04}
O.~Potonni\'{e}e.
\newblock A decentralized privacy-enabling TV personalization framework.
\newblock In {\em Proc. of European Conf. on Interactive Television}, 2004.

\bibitem[SCL{\etalchar{+}}05]{Shna05}
V.~Shnayder, B.~Chen, K.~Lorincz, T.R.F.~Fulford-Jones, and M.~Welsh.
\newblock Sensor Networks for Medical Care.
\newblock {\em Harvard University Technical Report}, TR-08-05, 2005.

\bibitem[WLLP01]{Warn01}
B.~Warneke, M.~Last, B.~Liebowitz, and K.S.J.~Pister.
\newblock Smart Dust: Communicating with a Cubic-Millimeter Computer.
\newblock {\em IEEE Computer}, 34(1), 2001.

\bibitem[DOOM01]{DoomC01}
C.~Doom.
\newblock Get Smart: How Intelligent Technology Will Enhance Our World.
\newblock {\em Computer Sciences Corporation}, 2001.

\bibitem[SDC05]{Spence05}
M.~Spence, C.~Driver, and S.~Clarke.
\newblock Sharing Context History in Mobile, Context-Aware Trails-Based Applications.
\newblock In {\em Proc. of the 1st Intl. Workshop on Exploiting Context Histories in Smart Environments}, 2005.

\bibitem[WWP05]{Wilson05}
D.H.~Wilson, D.~Wyatt, and M.~Philipose.
\newblock Using Context History for Data Collection in the Home.
\newblock In {\em Proc. of the 1st Intl. Workshop on Exploiting Context Histories in Smart Environments}, 2005.

\bibitem[LANG01]{Langheinrich01}
M.~Langheinrich.
\newblock Privacy by Design - Principles of Privacy-Aware Ubiquitous Systems.
\newblock In {\em Proc. of Ubicomp}, 2001.

\bibitem[OECD04]{TechPDF04}
OECD. \newblock The International Legal Framework for Data Protection and its Transportation to Developing Transitional Countries.
\newblock http://www.internetpolicy.net/ privacy/20041228privacy.pdf, 2004.

\bibitem[GLLR05]{FBI05}
L.A.~Gordon, M.P.~Loeb, W.~Lucyshyn, and R.~Richardson.
\newblock CSI/FBI Computer Crime and Security Survey.
\newblock http://i.cmpnet.com/gocsi/db\_area/pdfs/fbi/FBI2005.pdf, 2005.

\bibitem[CKR11]{Chaudhuri11}
S.~Chaudhuri, R.~Kaushik, and R.~Ramamurthy
\newblock Database Access Control {\&} Privacy: Is There A Common Ground?
\newblock In {\em Proc. of CIDR}, USA, 2011.

\bibitem[RSK{\etalchar{+}}10]{Roy10}
I.~Roy, S.~Setty, A.~Kilzer, V.~Shmatikov, and E.~Witchel.
\newblock Airavat: Security and Privacy for MapReduce.
\newblock In {\em Proc. of NSDI}, 2010.

\bibitem[CKS07]{Chaudhuri07}
S.~Chaudhuri, T. Dutta, and S. Sudarshan.
\newblock Fine Grained Authorization Through Predicated Grants.
\newblock In {\em Proc. of ICDE}, 2007.

\bibitem[KRS07]{Kabra07}
G.~Kabra, R.~Ramamurthy, and S.~Sudarshan.
\newblock Redundancy and Information Leakage in Fine-Grained Access Control.
\newblock In {\em Proc. of SIGMOD}, 2006.

\bibitem[LAMP74]{Lampson74}
B.W.~Lampson.
\newblock Protection.
\newblock {\em SIGOPS Oper. Syst. Rev.}, 8(1):18--24, 1974.

\bibitem[SAND94]{Sandhu94}
R.S.~Sandhu
\newblock Relational Database Access Controls.
\newblock Handbook of Information Security Management, Auerbach Pub-
lishers, 1994, pp 145--160.

\bibitem[SCFY96]{Sandhu96}
R.S.~Sandhu, E.J.~Coyne, H.L.~Feinstein, and C.E.~Youman.
\newblock Role-based Access Control Models.
\newblock {\em Computer}, 29(2):38--47, 1996.

\bibitem[FK92]{Ferraiolo92}
D.~Ferraiolo and D.~Kuhn.
\newblock Role-based Access Control.
\newblock In {\em Proc. of the Computer Security Conference,} 1992.

\bibitem[BBL05]{Byun05}
J.W.~Byun, E.~Bertino, and N.~Li.
\newblock Purpose-based Access Control of Complex Data for Privacy Protection.
\newblock In {\em Proc. of the 10th ACM symposium on Access Control Models and Technologies},
USA, pp 102-110, 2005.

\bibitem[P3P05]{p3ptoolbox05}
P3P~Toolbox.
\newblock What is P3P and How Does it Work?
\newblock http://www.p3ptoolbox.org/ guide/section2.shtml, 2005.

\bibitem[W3C07]{W3CP3P07}
\newblock Platform for Privacy Preferences {(P3P)} Project -
Enabling smarter Privacy Tools for the Web
\newblock http://www.w3.org/P3P/, 2007.

\bibitem[W3C02]{W3C02}
W3C.
\newblock A P3P Preference Exchange Language 1.0 (APPEL1.0).
\newblock http://www.w3.org/ TR/P3P-preferences/, 2002

\bibitem[AKS{\etalchar{+}}03]{Agrawal03}
R.~Agrawal, J.~Kiernan, R.~Srikant, and Y.~Xu.
\newblock Implementing {P3P} Using Database Technology.
\newblock In {\em Proc. of ICDE}, pp 595--606, 2003.

\bibitem[CRAN03]{Cranor03}
L.~Cranor.
\newblock {P3P}: Making Privacy Policies More Useful.
\newblock {\em IEEE Security {\&} Privacy Magazine}, 1(6):50--55, 2003.

\bibitem[AHKS]{Ashley02}
P.~Ashley, S.~Hada, G.~Karjoth, and M.~Schunter.
\newblock {E-P3P} Privacy Policies and Privacy Authorization.
\newblock In {\em Proc. of the ACM workshop on Privacy in the Electronic Society}, USA,
pp 103--109, 2002.

\bibitem[GR00]{Grimm02}
R.~Grimm and A.~Rossnagel.
\newblock Can {P3P} Help to Protect Privacy Worldwide?
\newblock In {\em Proc. of the ACM workshop on Multimedia}, USA,
pp 157--160, 2000.

\bibitem[ANDE08]{Anderson08}
R.~Anderson.
\newblock Security Engineering: A Guide to Building Dependable Distributed Systems.
\newblock John Wiley, 2008.

\bibitem[US12]{US12}
Dept.~of~Justice.
\newblock Privacy Act of 1974.
\newblock http://www.justice.gov/opcl/privacyact1974.htm, USA, 2012.

\bibitem[EC12]{European12}
European~Commission.
\newblock REGULATION OF THE EUROPEAN PARLIAMENT AND OF THE COUNCIL
on the protection of individuals with regard to the processing of personal data and on
the free movement of such data (General Data Protection Regulation).
\newblock http://ec.europa.eu/justice/data-protection/document/review2012/com\_2012\_11\_en.pdf, 2012.

\bibitem[GOLD04]{Goldreich04}
O.~Goldreich.
\newblock Foundations of Cryptography: Volume 2 (Basic Applications).
\newblock Cambridge university press, 2004.

\bibitem[JONK03]{Jon03}
W.~Jonker.
\newblock  {XML} and Secure Data Managament in an Ambient World.
\newblock {\em Computer Systems Science \& Engineering}, 18(5), 2003.

\bibitem[HEER10]{Harod2010}
H.~van~Heerde.
\newblock Privacy-Aware Data Management by Means of Data Degradation -
Making Private Data Less Sensitive Over Time.
\newblock PhD Thesis, CTIT, University of Twente, The Netherlands, 2010.

\bibitem[BP02]{BP2002}
L.~Bouganim and P.~Pucheral.
\newblock Chip-Secured Data Access: Confidential Data on Untrusted Servers.
\newblock In {\em Proc. of VLDB}, 2002.

\bibitem[HLLM02]{Haci02}
H.~Hacig{\"{u}}m{\"{u}\c{s}}, B.~Lyer, C.~Li, and S.~Mehrotra,
\newblock Executing {SQL} Over Encrypted Data in the Database-Service-Provider Model.
\newblock In {\em Proc. of ACM SIGMOD}, USA, pp 216--227, 2002.

\bibitem[HLM02]{Haci02b}
H.~Hacig{\"{u}}m{\"{u}\c{s}}, B.~Lyer, and S.~Mehrotra.
\newblock Providing Database as a Service.
\newblock In {\em Proc. of ICDE}, 2002.

\bibitem[W3C08]{W3C08}
World Wide Web Consortium.
\newblock Extensible Markup Language ({XML}) 1.0 (Fifth Edition),
\newblock http://www.w3.org/TR/REC-xml, 2008.

\bibitem[W3C02a]{W3C02c}
World Wide Web Consortium.
\newblock {XML} Encryption Syntax and Processing.
\newblock http://www.w3.org/TR/xmlenc-core/, 2002.

\bibitem[W3C02b]{W3C02d}
World Wide Web Consortium.
\newblock {XML} Encryption Requirements.
\newblock http://www.w3.org/TR/ xml-encryption-req, 2002.

\bibitem[W3C10]{W3C02a}
World Wide Web Consortium.
\newblock {XML} Path Language ({XPath}) 2.0 (Second Edition).
\newblock http://www.w3.org/TR/xpath20/, 2010.

\bibitem[CFCR02]{Chan02}
C.~Chan, P.~Felber, M.~Carofalakis, and R.~Rastogi.
\newblock Efficient Filtering of {XML} Documents with {XPath} Expressions,
\newblock In {\em Proc. of ICDE}, USA, 2002.

\bibitem[AF00]{Alti00}
M.~Altinel and M.~Franklin.
\newblock Efficient Filtering of {XML} Documents for Selective
                Dissemination of Information.
\newblock In {\em Proc. of VLDB}, Egypt, pp 53--64, 2000.

\bibitem[SWP00]{Song00}
D.~Song, D.~Wagner, and A.~Perrig.
\newblock Practical Techniques for Searches on Encrypted Data.
\newblock In {\em Proc. of the IEEE Symposium on Security and Privacy}, 2000.

\bibitem[FJ04]{FengJonker04}
L.~Feng and W.~Jonker.
\newblock Preparations for Encrypted XML Metadata Querying.
\newblock {\em Intl. J. of Computer Systems, Science \& Engineering},
19(3/4):95--103, 2004.

\bibitem[BFD{\etalchar{+}}04]{Brinkman04}
R.~Brinkman, L.~Feng, J.M.~Doumen, P.~Hartel, and W.~Jonker.
\newblock Efficient Tree Search in Encrypted Data.
\newblock {\em Intl. J. of Information Systems Security}, 13(3):14-21, 2004.

\bibitem[GRUS02]{Grust02}
T.~Grust.
\newblock Accelerating Xpath Location Steps.
\newblock In {\em Proc. of SIGMOD}, USA, pp 109--120, 2002.

\bibitem[GKT03]{Grust03}
T.~Grust, M.~van~Keulen, and J.~Teubner.
\newblock Staircase join: Teach a relational dbms to watch its (axis) steps.
\newblock In {\em Proc. of VLDB}, Germany, 2003.

\bibitem[CF04]{Chandrasekaran04}
S.~Chandrasekaran and M.J.~Franklin.
\newblock Remembrance of Streams Past: Overload-Sensitive Management of Archived Streams.
\newblock In {\em Proc. of VLDB}, 2004.

\bibitem[BB06]{Byun06}
J.W.~Byun and E.~Bertino.
\newblock Micro-views, or on how to protect privacy
while enhancing data usability: concepts and challenges.
\newblock {\em SIGMOD Record}, 35(1):9--13, 2006.

\bibitem[BBL05]{Bertino05}
E.~Bertino, J.W.~Byun, and N.~Li.
\newblock Privacy-Preserving Database Systems.
\newblock In {\em Proc. of FOSAD}, pp 178-206, 2005.

\bibitem[AKSX02]{Agrawal02}
R.~Agrawal, J.~Kiernan, R.~Srikant, and Y.~Xu.
\newblock Hippocratic Databases.
\newblock In {\em Proc. of VLDB}, Hong Kong, 2002.

\bibitem[LANG02]{Langheinrich02}
M.~Langheinrich.
\newblock A Privacy Awareness System for Ubiquitous Computing Environments.
\newblock In {\em Proc. of Ubicomp}, 2002.

\bibitem[VBF{\etalchar{+}}04]{Verykios04}
V.S.~Verykios, E.~Bertino, I.N.~Fovino, L.P.~Provenza, Y.~Saygin, and Y.~Theodoridis.
\newblock State-of-the-art in Privacy Preserving Data Mining.
\newblock {\em SIGMOD Record}, 33, 2004.

\bibitem[AW8902]{Adam89}
N.R.~Adam and J.C.~Worthmann.
\newblock Security-Control Methods for Statistical Databases: a Comparative Study.
\newblock {\em ACM Computing Surveys}, 21(4), 1989.

\bibitem[AS00]{Agrawal00}
R.~Agrawal and R.~Srikant.
\newblock Privacy-Preserving Data Mining.
\newblock In {\em Proc. of ACM SIGMOD}, 2000.

\bibitem[SS98a]{Samarati98a}
P.~Samarati and L.~Sweeney.
\newblock Generalizing Data to Provide Anonymity When Disclosing Information.
\newblock In {\em ACM Symposium on Principles of Database Systems}, 1998.

\bibitem[SS98b]{Samarati98b}
P.~Samarati and L.~Sweeney.
\newblock Protecting Privacy When Disclosing Information: k-Anonymity and Its Enforcement Through
Generalization and Suppression.
\newblock In {\em IEEE Symposium on Research in Security and Privacy}, 1998.

\bibitem[SWEE02a]{Sweeney02a}
L.~Sweeney.
\newblock Achieving k-Anonymity Privacy Protection using Generalization and Suppression.
\newblock {\em Int. Journal on Uncertainty, Fuzziness, and Knowledge-based Systems}, 10(5), 2002.

\bibitem[SWEE02b]{Sweeney02b}
L.~Sweeney.
\newblock k-Anonymity: a Model for Protecting Privacy.
\newblock {\em Int. Journal on Uncertainty, Fuzziness and Knowledge-based Systems}, 10(5), 2002.

\bibitem[MMZ05]{Massacci05}
F.~Massacci, J.~Mylopoulos, and N.~Zannone.
\newblock Minimal Disclosure in Hierarchical Hippocratic Databases with Delegation.
\newblock In {\em Proc. of ESORICS}, pp 438--454, 2005.


\bibitem[UN90]{United90}
United Nations.
\newblock Guidelines on the Use of Computerized Personal Files.
\newblock Economic and Social Council, resolution 1990/38, 1990.

\bibitem[HL04]{Hong04}
J.I.~Hong and J.A.~Landay.
\newblock An Architecture for Privacy-Sensitive Ubiquitous Computing.
\newblock In {\em Proc. of MobiSys}, 2004.

\bibitem[IA05]{Iachello05}
G.~Iachello and G.D.~Abowd.
\newblock Privacy and Proportionality: Adapting Legal Evaluation Techniques to Inform
Design in Ubiquitous Computing.
\newblock In {\em Proc. of CHI}, 2005.

\bibitem[LMD03]{Lederer03}
S.~Lederer, J.~Mankoff, and A.K.~Dey.
\newblock Who Wants to Know What When? Privacy Preference Determinants in Ubiquitous Computing.
\newblock In {\em Proc. of CHI}, 2003.




\end{thebibliography}
